%\s{The community}
\section{Сообщество}

% Despite the fact that I used ``I'' in the first part of the book, LYSA
% is actually a community project, and many people participate in the
% writing of this book.
Опуская тот факт, что я~использую \q{Я} в~первой части книги, LYSA
является проектом сообщества и~довольно много людей участвуют
в~написании этой книги.

% If you want to talk to us, or to other math people, come see us in {\tt
% \#lysa} on Freenode. If you don't know what IRC is, or you don't have a
% client set up, you can connect through
% \link{http://webchat.freenode.net/?channels=lysa}{Freenode's webchat}.
Если вы~хотите пообщаться с~нами или другими математиками, приходите
к~нам в~чат {\tt \#lysa} на~Freenode. Если вы~не~знаете, что такое IRC,
или вы~не~знаете как настроить клиент "--- вы~можете зайти в~чат через
\link{http://webchat.freenode.net/?channels=lysa}{вебчат Freenode}.

% If you have any questions about LYSA (or math), feel free to ask in the
% IRC channel ({\tt \#lysa} on FreeNode in case you forgot).
Если у~вас возникли любые вопросы по~LYSA (или математике), пожалуйста,
задавайте их~в~чате ({\tt \#lysa} на~FreeNode, если вы~забыли где).

% If you want to submit a correction, or have some issue, or want to add
% some content, really anything having to do with the content of the book,
% you can visit \link{https://github.com/learnyou/lysa}{our GitHub
% page}. We also have a \link{http://learnyou.org}{website} and a
% \link{https://lysa.reddit.com/}{community on Reddit}.
Если вы~хотите исправить что-либо, или заметили какую-либо проблему,
или хотите добавить какой-то материал "--- что угодно, связанное
с~содержимым книги "--- вы~можете зайти
на~\link{https://github.com/gazay/lysa}{нашу русскоязычную GitHub
страницу} или на~\link{https://gitlab.com/lysa/lysa}{оригинальную
страницу книги}. У~нас также есть \link{http://learnyou.org}{по
недоделанный сайт} и~\link{https://lysa.reddit.com/}{сообщество на~Reddit}.

% TODO: translate
% \ss{Freedom}
\subsection{Freedom}

This book is open-source. That means a number of things:

\begin{enumerate}
\item You are free to use this book as you like.
\item You are free to modify the book as you wish. The source is
      available at \btrurl{https://github.com/learnyou/lysa}.
\item You are free to redistribute and/or sell exact copies of this book
      as you wish.
\item You are free to redistribute and/or sell modified copies of this
      book as you wish.
\end{enumerate}

If, for instance, you are a schoolteacher and want to use this for your
class, you are free to edit it to your liking and give the modified copy
to your students. The only string I attach is, you have to allow anyone
to whom you give the book do the same thing (i.e. they have to be free
to copy/modify/change your version). 
